---
title: "timeline_subsets_analysis"
output: html_document
date: "2024-07-23"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Timelines - Data Subset(s) Analysis

Probing the data at a deeper scale - creating a viewable data frame for each combination\* and testing each data subset for normality, using Shapiro Wilk.

*\*total possible combinations: 12 [Urdu - LR + TB + RL; English (primary) - LR + TB + RL; etc.]*

Note:

## General Setup

Packages and ibraries to import, global variables, reading in data file.

```{r echo=FALSE, message=FALSE, results='hide'}
#TODO: Eliminate reundandant packages. 
# (YFA: i added these as i needed. It may be the case that packages are repeated, eg. tidyverse has ggplot2 and dplyr.) 

# import libraries
library(readxl)
library(dplyr)
library(purrr)
library(tidyverse)
library(skimr)
library(ggplot2)
library(ggpubr)
library(RColorBrewer)
library(gridExtra) #fyi: masked from dplyr, to specify function paths #TODO
```

**Importing data file:**

1.  Rename data file with ALL responses data across all 3 groups (EE, EU, EA) as "analysis_data"
2.  Open the data file in Excel and
    1.  remove the second row that contains question text. This is not needed.
    2.  ensure all responses are from 7th July 2024 and onward. Any responses collected before are pilot runs and not true responses.
    3.  Rename the TB question columns to not have the "#1_1" character in them. I am not sure why but this is how Qualtrics exports data for the side by side question type.
        1.  `Find "#1_1"` (find all) and then `Replace with ""` (replace all).

```{r echo=FALSE}

# Reading data from data file
pilotDF <- read_excel("./data/analysis_data.xlsx")

#cleaning data (exclude unfinished responses)
pilotDF <- pilotDF %>%
  filter(pilotDF$Finished != "False")

# Defining global variables
MAX_SCORE <- 12
SCORE_VALUE <- 1

#variables subject to change as we get more responses:

#no. of total respondants
SAMPLE_SIZE <- nrow(pilotDF) 

#no. of responses that answer with English as primary lang
eng_primary_size <- pilotDF %>%
  filter(pilotDF$`CF EE` == "I AGREE") %>%
  nrow() 

#no. of responses that answer with Urdu as primary lang:
urdu_primary_size <- pilotDF %>%
  filter(pilotDF$`EU CF` == "I AGREE") %>%
  nrow() 

#no. of responses that answer with Arabic as primary lang
arb_primary_size <- pilotDF %>%
  filter(pilotDF$`EA CF` == "I AGREE") %>%
  nrow() 

# printing out values for html/ pdf
paste0("Total Sample Size: ", SAMPLE_SIZE)
paste0("English(primary) pool size: ", eng_primary_size)
paste0("Urdu pool size: ", urdu_primary_size)
paste0("Arabic pool size: ", arb_primary_size)
```

## Defining Functions/ Procedures

### Summing Accuracies

Sums up accuracy scores for provided language and orientation group (prefix) from dataset.

Maximum possible score for any condition is 12. Calculates weighed accuracy (achieved score divided by 12) for provided prefix and for each participant.

\*Weighed accuracy approach to account for negative marking of the questions (-1, -2, -5, -10).

```{r}
# Function to process accuracy data
# RETURNS accuracy percentage (scored/12) for lanuage+orientation combo
acc_sum <- function(df, prefix) {
  
  # Select specific columns
  selected_columns <- df %>%
    select(matches(paste0("^", prefix, " - Q[1-6]$")))
  
  # Converting character vectors to numeric
  data_numeric <- lapply(selected_columns, function(column) as.numeric(column))
  
  # Combine the lists into a data frame to facilitate row-wise operations
  data_numeric_df <- as.data.frame(data_numeric)
  # this creates a data frame for the specified language-timeline (prefix) combo.
  # will end up creating 9 data frames (3 per language, TB, RL, LR)
  # each data frame will have [SAMPLE_SIZE] rows * 12 columns (questions)
  
  # Filter out rows where all values are NA #
  data_filtered <- data_numeric_df[rowSums(is.na(data_numeric_df)) != ncol(data_numeric_df), ]
  # the no. of rows for the data frame will match the pool size for the specified langugae participants
  # eg. Urdu speakers df will have [urdu_primary_size] rows by 12 columns
  

  # Replace negative values with zero 
  data_filtered[data_filtered < 0] <- 0
  # for current analysis purposes: not interested in analysing performance by quest. difficulty
  
  # List to store sums of each index across columns
  sums <- numeric(nrow(data_filtered))
  
  # Calculate and store sums of each index across columns
  for (i in seq_along(sums)) {
    sums[i] <- sum(data_filtered[i, ], na.rm = TRUE)
  }
  #sums can range bw 0 to 12
  #print(sums) #debugging
  
  #accuracy for each participant
  accuracy_raw <- sums / MAX_SCORE
  
  # return accuracy + raw scores
  return(list(accuracy = accuracy_raw, sums = sums))
}
```

### Summing Times

Sums up time spent on questions in a provided language and orientation group (prefix) from dataset.

Sums up time taken to complete the 12 questions in the given prefix for each participant.

```{r}
# Function to process time data
time_sum <- function(df, prefix) {
  
  # Select specific columns
  selected_columns <- df %>%
    select(matches(paste0("^", prefix, " - Q[1-6] Time_Page Submit$")))
  
  # Converting character vectors to numeric
  data_numeric <- lapply(selected_columns, function(column) as.numeric(column))
  
  # Combine the lists into a data frame to facilitate row-wise operations
  data_numeric_df <- as.data.frame(data_numeric)
  
  # Filter out rows where all values are NA
  data_filtered <- data_numeric_df[rowSums(is.na(data_numeric_df)) != ncol(data_numeric_df), ]
  
  # List to store sums of each index across columns
  sums <- numeric(nrow(data_filtered))
  
  # Calculate and store sums of each index across columns
  for (i in seq_along(sums)) {
    sums[i] <- sum(data_filtered[i, ], na.rm = TRUE)
  }
  
  return(sums)
}
```

### Extra: Box Plots

Optional function to see data distribution for provided prefix, for visualization purposes only.

TODO: adjust y-scales for larger values. Plots are almost useless without that.

```{r}
box_plot <- function(bp_data){
  # Plot weighted accuracy
  ggboxplot(bp_data, x="metric", y="value",
            color = "metric", palette=c("#00AFBB","#E7B800"),
            ylab= "Value", xlab="Metric")
  
 #print(bp_data)
}
```

### Extra: Bar Graph

Optional function to see distribution of aggregated mean values for a language group.

```{r}
bar_plot <- function(data, title, col_palette){
  ggplot(data, aes(x = orientation, y = metric, fill = orientation)) + 
    geom_bar(stat = "identity") + 
    labs(title = title, x = "Orientation", y = "Mean Value") +
    theme_minimal() + 
    scale_fill_brewer(palette=col_palette)
}
```

## Analysing English12

**(Secondary Language/ Universal)**

```{r echo=FALSE}
participant_ID <- rep(1:SAMPLE_SIZE, times=2)
```

### LEFT-RIGHT

Uses functions defined above to aggregate data - time and accuracy sums - for the English Left-Right orientation. Implements the **Shapiro Wilk test** to determine if data is normally distributed, assuming alpha = 0.05.

*p-value \> alpha to confirm normality.*

\*Uses columns **ELR1 and ELR2** in dataset for this purpose.

```{r echo=FALSE}
#Calculating weighted accuracy
ELR12_acc <- acc_sum(pilotDF, "ELR[12]")
#print("LR Accuracy Normality Check")
shapiro.test(ELR12_acc)

#Q: do we need to test this data subseet for normality?

#Summing times
ELR12_time <- time_sum(pilotDF, "ELR[12]")
shapiro.test(ELR12_time)

#creating df
ELR12_df <- data.frame(
  p_id = participant_ID,
  metric = rep(c("time", "accuracy"), each=SAMPLE_SIZE),
  value = c(ELR12_time,ELR12_acc)
)

# box blot distribution
#box_plot(ELR12_df)
```

### RIGHT - LEFT

Uses functions defined above to aggregate data - time and accuracy sums - for the English Right-Left orientation. Implements the **Shapiro Wilk test** to determine if data is normally distributed, assuming alpha = 0.05.

\*Uses columns **ERL1 and ERL2** in dataset for this purpose.

```{r echo=FALSE}
#Calculating weighted accuracy
ERL12_acc <- acc_sum(pilotDF, "ERL[12]")
#print("RL Accuracy Normality Check")
shapiro.test(ERL12_acc)

#Summing times
ERL12_time <- time_sum(pilotDF, "ERL[12]")
#print("RL Time Normality Check")
shapiro.test(ERL12_time)

#creating df for plot
ERL12_df <- data.frame(
  p_id = participant_ID,
  metric = rep(c("time", "accuracy"), each=SAMPLE_SIZE),
  value = c(ERL12_time, ERL12_acc)
)

# box blot distribution
#box_plot(ERL12_df)
```

### TOP - BOTTOM

Uses functions defined above to aggregate data - time and accuracy sums - for the English Top-Bottom orientation. Implements the **Shapiro Wilk test** to determine if data is normally distributed, assuming alpha = 0.05.

\*Uses columns **ETB1 and ETB2** in dataset for this purpose.

```{r echo=FALSE}
#Calculating weighted accuracy
ETB12_acc <- acc_sum(pilotDF, "ETB[12]")
#print("TB Accuracy Normality Check")
shapiro.test(ETB12_acc)

#Summing times
ETB12_time <- time_sum(pilotDF, "ETB[12]")
#print("TB Time Normality Check")
shapiro.test(ETB12_time)

#creating df for plot
ETB12_df <- data.frame(
  p_id = participant_ID,
  metric = rep(c("time", "accuracy"), each=SAMPLE_SIZE),
  value = c(ETB12_time, ETB12_acc)
)

# box blot distribution
#box_plot(ERL12_df)
```

#### Bar Plot(s) [extra]

```{r echo=FALSE}

mean_time_data <- data.frame(
  orientation=c("LR","TB","RL"),
  metric = c(mean(ELR12_time, na.rm = TRUE), mean(ETB12_time, na.rm = TRUE), mean(ERL12_time, na.rm = TRUE))
)

mean_acc_data <- data.frame(
  orientation=c("LR","TB","RL"),
  metric = c(mean(ELR12_acc, na.rm = TRUE), mean(ETB12_acc, na.rm = TRUE), mean(ERL12_acc, na.rm = TRUE))
)

bar_plot(mean_time_data,paste("Mean of Time Spent (in seconds) - English; participants:", SAMPLE_SIZE), "Accent")
bar_plot(mean_acc_data, paste("Mean of Scored Accuracy - English; participants:", SAMPLE_SIZE), "Set3")
```

### Merging Data (LR, RL, TB)

Merging data from all three orientations in to one data frame for statistical t-testing. A preview of how the frame looks like can be seen below.

```{r echo=FALSE}
# Merge the data frames
df_ENG_ALL2 <- ELR12_df %>%
  rename(value_LR = value) %>%
  full_join(ERL12_df %>% rename(value_RL = value), by = c("p_id", "metric")) %>%
  full_join(ETB12_df %>% rename(value_TB = value), by = c("p_id", "metric"))

# display merged data frame
head(df_ENG_ALL2)

```

***Q: What orientation does \<LANGUAGE\> do better with?***

# Analysing English34

**(Primary Language)**

Analyzing performance who chose English as their primary (/ native/ first) language. Calculations and statistical testing to *figure out what orientation (TB, LR, or RL) is best for the English language*.

```{r echo=FALSE}
participant_ID <- rep(1:eng_primary_size, times=2)
```

Thought: This creating data subsets + merging datasets could very well be in a function instead of doing this for all 4 language groups (TODO for when I'm bored/stuck)

### LEFT-RIGHT

Uses functions defined above to aggregate data - time and accuracy sums - for the English Left-Right orientation. Implements the **Shapiro Wilk test** to determine if data is normally distributed, assuming alpha = 0.05.

\*Uses columns **ELR3 and ELR4** in dataset for this purpose.

```{r echo=FALSE}
#Calculating weighted accuracy
ELR34_acc <- acc_sum(pilotDF, "ELR[34]")
#print("LR Accuracy Normality Check")
shapiro.test(ELR34_acc)

#Summing times
ELR34_time <- time_sum(pilotDF, "ELR[34]")
shapiro.test(ELR34_time)

#creating df
ELR34_df <- data.frame(
  p_id = participant_ID,
  metric = rep(c("time", "accuracy"), each=eng_primary_size),
  value = c(ELR34_time,ELR34_acc)
)

# box blot distribution
#box_plot(ELR34_df)
```

### RIGHT - LEFT

Uses functions defined above to aggregate data - time and accuracy sums - for the English Right-Left orientation. Implements the **Shapiro Wilk test** to determine if data is normally distributed, assuming alpha = 0.05.

\*Uses columns **ERL3 and ERL4** in dataset for this purpose.

```{r echo=FALSE}
#Calculating weighted accuracy
ERL34_acc <- acc_sum(pilotDF, "ERL[34]")
#print("RL Accuracy Normality Check")
shapiro.test(ERL34_acc)

#Summing times
ERL34_time <- time_sum(pilotDF, "ERL[34]")
#print("RL Time Normality Check")
shapiro.test(ERL34_time)

#creating df for plot
ERL34_df <- data.frame(
  p_id = participant_ID,
  metric = rep(c("time", "accuracy"), each=eng_primary_size),
  value = c(ERL34_time, ERL34_acc)
)

# box blot distribution
#box_plot(ERL34_df)
```

### TOP - BOTTOM

Uses functions defined above to aggregate data - time and accuracy sums - for the English Top-Bottom orientation. Implements the **Shapiro Wilk test** to determine if data is normally distributed, assuming alpha = 0.05.

\*Uses columns **ETB3 and ETB4** in dataset for this purpose.

```{r echo=FALSE}
#Calculating weighted accuracy
ETB34_acc <- acc_sum(pilotDF, "ETB[34]")
#print("TB Accuracy Normality Check")
shapiro.test(ETB34_acc)

#Summing times
ETB34_time <- time_sum(pilotDF, "ETB[34]")
#print("TB Time Normality Check")
shapiro.test(ETB34_time)

#creating df for plot
ETB34_df <- data.frame(
  p_id = participant_ID,
  metric = rep(c("time", "accuracy"), each=eng_primary_size),
  value = c(ETB34_time, ETB34_acc)
)

# box blot distribution
#box_plot(ERL34_df)
```

#### Bar Plot(s) [extra]

```{r echo=FALSE}

mean_time_data <- data.frame(
  orientation=c("left-right","top-bottom","right-left"),
  metric = c(mean(ELR34_time, na.rm = TRUE), mean(ETB34_time, na.rm = TRUE), mean(ERL34_time, na.rm = TRUE))
)

mean_acc_data <- data.frame(
  orientation=c("left-right","top-bottom","right-left"),
  metric = c(mean(ELR34_acc, na.rm = TRUE), mean(ETB34_acc, na.rm = TRUE), mean(ERL34_acc, na.rm = TRUE))
)

bar_plot(mean_time_data,paste("Mean of Time Spent (in seconds) - English; participants:", eng_primary_size), "Set2")
bar_plot(mean_acc_data, paste("Mean of Scored Accuracy - English; participants:", eng_primary_size),"Blues")
```

### Merging Data (LR, RL, TB)

Merging data from all three orientations in to one data frame for statistical t-testing. A preview of how the frame looks like can be seen below.

```{r echo=FALSE}
# Merge the data frames
df_ENG34 <- ELR34_df %>%
  rename(value_LR = value) %>%
  full_join(ERL34_df %>% rename(value_RL = value), by = c("p_id", "metric")) %>%
  full_join(ETB34_df %>% rename(value_TB = value), by = c("p_id", "metric"))

# display merged data frame
head(df_ENG34 )

```

# Urdu

Analyzing performance who chose Urdu as their primary (/ native/ first) language. Calculations and statistical testing to *figure out what orientation (TB, LR, or RL) is best for the Urdu language*.

```{r echo=FALSE}
participant_ID <- rep(1:urdu_primary_size, times=2)
```

### LEFT-RIGHT

Uses functions defined above to aggregate data - time and accuracy sums - for the Urdu Left-Right orientation. Implements the **Shapiro Wilk test** to determine if data is normally distributed, assuming alpha = 0.05.

\*Uses columns **ULR1 and ULR2** in dataset for this purpose.

```{r}
#Calculating weighted accuracy
ULR12_acc <- acc_sum(pilotDF, "ULR[12]")
#print("LR Accuracy Normality Check")
shapiro.test(ULR12_acc)

#Summing times
ULR12_time <- time_sum(pilotDF, "ULR[12]")
shapiro.test(ULR12_time)

#creating df
ULR12_df <- data.frame(
  p_id = participant_ID,
  metric = rep(c("time", "accuracy"), each=urdu_primary_size),
  value = c(ULR12_time,ULR12_acc)
)

# box blot distribution
#box_plot(ULR12_df)
```

### RIGHT - LEFT

Uses functions defined above to aggregate data - time and accuracy sums - for the Urdu Right-Left orientation. Implements the **Shapiro Wilk test** to determine if data is normally distributed, assuming alpha = 0.05.

\*Uses columns **URL1 and URL2** in dataset for this purpose.

```{r}
#Calculating weighted accuracy
URL12_acc <- acc_sum(pilotDF, "URL[12]")
#print("RL Accuracy Normality Check")
shapiro.test(URL12_acc)

#Summing times
URL12_time <- time_sum(pilotDF, "URL[12]")
#print("RL Time Normality Check")
shapiro.test(URL12_time)

#creating df for plot
URL12_df <- data.frame(
  p_id = participant_ID,
  metric = rep(c("time", "accuracy"), each=urdu_primary_size),
  value = c(URL12_time, URL12_acc)
)

# box blot distribution
#box_plot(URL12_df)
```

### TOP - BOTTOM

Uses functions defined above to aggregate data - time and accuracy sums - for the Urdu Top-Bottom orientation. Implements the **Shapiro Wilk test** to determine if data is normally distributed, assuming alpha = 0.05.

\*Uses columns **UTB1 and UTB2** in dataset for this purpose.

```{r}
#Calculating weighted accuracy
UTB12_acc <- acc_sum(pilotDF, "UTB[12]")
#print("TB Accuracy Normality Check")
shapiro.test(UTB12_acc)

#Summing times
UTB12_time <- time_sum(pilotDF, "UTB[12]")
#print("TB Time Normality Check")
shapiro.test(UTB12_time)

#creating df for plot
UTB12_df <- data.frame(
  p_id = participant_ID,
  metric = rep(c("time", "accuracy"), each=urdu_primary_size),
  value = c(UTB12_time, UTB12_acc)
)

# box blot distribution
#box_plot(URL12_df)
```

#### Bar Plot(s) [extra]

```{r echo=FALSE}

mean_time_data <- data.frame(
  orientation=c("left-right","top-bottom","right-left"),
  metric = c(mean(ULR12_time, na.rm = TRUE), mean(UTB12_time, na.rm = TRUE), mean(URL12_time, na.rm = TRUE))
)

mean_acc_data <- data.frame(
  orientation=c("left-right","top-bottom","right-left"),
  metric = c(mean(ULR12_acc, na.rm = TRUE), mean(UTB12_acc, na.rm = TRUE), mean(URL12_acc, na.rm = TRUE))
)

bar_plot(mean_time_data,paste("Mean of Time Spent (in seconds) - Urdu; participants:", urdu_primary_size), "Accent")
bar_plot(mean_acc_data, paste("Mean of Scored Accuracy - Urdu; participants:", urdu_primary_size), "Blues")
```

### Merging Data (LR, RL, TB)

Merging data from all three orientations in to one data frame for statistical t-testing. A preview of how the frame looks like can be seen below.

```{r echo=FALSE}
# Merge the data frames
df_URDU <- ULR12_df %>%
  rename(value_LR = value) %>%
  full_join(URL12_df %>% rename(value_RL = value), by = c("p_id", "metric")) %>%
  full_join(UTB12_df %>% rename(value_TB = value), by = c("p_id", "metric"))

# display merged data frame
head(df_URDU)

```

# Arabic

Analyzing performance who chose Arabic as their primary (/ native/ first) language. Calculations and statistical testing to *figure out what orientation (TB, LR, or RL) is best for the Arabic language*.

```{r echo=FALSE}
participant_ID <- rep(1:arb_primary_size, times=2)
```

### LEFT-RIGHT

Uses functions defined above to aggregate data - time and accuracy sums - for the Arabic Left-Right orientation. Implements the **Shapiro Wilk test** to determine if data is normally distributed, assuming alpha = 0.05.

\*Uses columns **ALR1 and ALR2** in dataset for this purpose.

```{r}
#Calculating weighted accuracy
ALR12_acc <- acc_sum(pilotDF, "ALR[12]")
#summary(ALR12_acc)
#print("LR Accuracy Normality Check")
shapiro.test(ALR12_acc)

#Summing times
ALR12_time <- time_sum(pilotDF, "ALR[12]")
shapiro.test(ALR12_time)

#creating df
ALR12_df <- data.frame(
  p_id = participant_ID,
  metric = rep(c("time", "accuracy"), each=arb_primary_size),
  value = c(ALR12_time,ALR12_acc)
)

# box blot distribution
#box_plot(ALR12_df)
```

### RIGHT - LEFT

Uses functions defined above to aggregate data - time and accuracy sums - for the Arabic Right-Left orientation. Implements the **Shapiro Wilk test** to determine if data is normally distributed, assuming alpha = 0.05.

\*Uses columns **ARL1 and ARL2** in dataset for this purpose.

```{r}
#Calculating weighted accuracy
ARL12_acc <- acc_sum(pilotDF, "ARL[12]")
#print("RL Accuracy Normality Check")
shapiro.test(ARL12_acc)

#Summing times
ARL12_time <- time_sum(pilotDF, "ARL[12]")
#print("RL Time Normality Check")
shapiro.test(ARL12_time)

#creating df for plot
ARL12_df <- data.frame(
  p_id = participant_ID,
  metric = rep(c("time", "accuracy"), each=arb_primary_size),
  value = c(ARL12_time, ARL12_acc)
)

# box blot distribution
#box_plot(ARL12_df)
```

### TOP - BOTTOM

Uses functions defined above to aggregate data - time and accuracy sums - for the Arabic Top-Bottom orientation. Implements the **Shapiro Wilk test** to determine if data is normally distributed, assuming alpha = 0.05.

\*Uses columns **ATB1 and ATB2** in dataset for this purpose.

```{r}
#Calculating weighted accuracy
ATB12_acc <- acc_sum(pilotDF, "ATB[12]")
#print("TB Accuracy Normality Check")
shapiro.test(ATB12_acc)

#Summing times
ATB12_time <- time_sum(pilotDF, "ATB[12]")
#print("TB Time Normality Check")
shapiro.test(ATB12_time)

#creating df for plot
ATB12_df <- data.frame(
  p_id = participant_ID,
  metric = rep(c("time", "accuracy"), each=arb_primary_size),
  value = c(ATB12_time, ATB12_acc)
)

# box blot distribution
#box_plot(ARL12_df)
```

#### Bar Plot(s) [extra]

```{r echo=FALSE}

mean_time_data <- data.frame(
  orientation=c("LR","TB","RL"),
  metric = c(mean(ALR12_time, na.rm = TRUE), mean(ATB12_time, na.rm = TRUE), mean(ARL12_time, na.rm = TRUE))
)

mean_acc_data <- data.frame(
  orientation=c("LR","TB","RL"),
  metric = c(mean(ALR12_acc, na.rm = TRUE), mean(ATB12_acc, na.rm = TRUE), mean(ARL12_acc, na.rm = TRUE))
)

bar_plot(mean_time_data,paste("Mean of Time Spent (in seconds) - Arabic; participants:", arb_primary_size), "Spectral")
bar_plot(mean_acc_data, paste("Mean of Scored Accuracy - Arabic; participants:", arb_primary_size), "Dark2")
```

### Merging Data (LR, RL, TB)

Merging data from all three orientations in to one data frame for statistical t-testing. A preview of how the frame looks like can be seen below.

```{r echo=FALSE}
# Merge the data frames
df_ARABIC <- ALR12_df %>%
  rename(value_LR = value) %>%
  full_join(ARL12_df %>% rename(value_RL = value), by = c("p_id", "metric")) %>%
  full_join(ATB12_df %>% rename(value_TB = value), by = c("p_id", "metric"))

# display merged data frame
head(df_ARABIC)
```
