---
title: "Timelines Analysis"
output: html_document
date: "2024-07-08"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Timeline Analysis

## General Setup

Packages and ibraries to import, global variables, reading in data file.

```{r message=FALSE, results='hide'}

# import libraries
library(readxl)
library(dplyr)
library(purrr)
library(tidyverse)
library(ggplot2)
library(ggpubr)
library(RColorBrewer)

# Reading data from data file
pilotDF <- read_excel("./data/pilot_analysis.xlsx")

# Defining global variables
MAX_SCORE <- 12

#variables subject to change as we get more responses:

#no. of total respondants
SAMPLE_SIZE <- nrow(pilotDF) 

#no. of responses that answer with English as primary lang
eng_primary_size <- pilotDF %>%
  filter(pilotDF$`CF EE` == "I AGREE") %>%
  nrow() 

#no. of responses that answer with Urdu as primary lang:
urdu_primary_size <- pilotDF %>%
  filter(pilotDF$`EU CF` == "I AGREE") %>%
  nrow() 

#no. of responses that answer with Arabic as primary lang
arb_primary_size <- pilotDF %>%
  filter(pilotDF$`EA CF` == "I AGREE") %>%
  nrow() 
```

## Defining Functions/ Procedures

### Summing Accuracies

Sums up accuracy scores for provided language and orientation group (prefix) from dataset.

Maximum possible score for any condition is 12. Calculates weighed accuracy (achieved score divided by 12) for provided prefix and for each participant.

\*Weighed accuracy approach to account for negative marking of the questions (-1, -2, -5, -10).

```{r}
# Function to process accuracy data
# RETURNS weighted accuracy
acc_sum <- function(df, prefix) {
  
  # Select specific columns
  selected_columns <- df %>%
    select(matches(paste0("^", prefix, " - Q[1-6]$")))
  
  # Converting character vectors to numeric
  data_numeric <- lapply(selected_columns, function(column) as.numeric(column))
  
  # Combine the lists into a data frame to facilitate row-wise operations
  data_numeric_df <- as.data.frame(data_numeric)
  
  # Filter out rows where all values are NA
  data_filtered <- data_numeric_df[rowSums(is.na(data_numeric_df)) != ncol(data_numeric_df), ]
  
  # List to store sums of each index across columns
  sums <- numeric(nrow(data_filtered))
  
  # Calculate and store sums of each index across columns
  for (i in seq_along(sums)) {
    sums[i] <- sum(data_filtered[i, ], na.rm = TRUE)
  }
  
  # Weighted accuracy for each participant
  weighted_accuracy <- sums / MAX_SCORE
  
  return(weighted_accuracy)
}
```

### Summing Times

Sums up time spent on questions in a provided language and orientation group (prefix) from dataset.

Sums up time taken to complete the 12 questions in the given prefix for each participant.

```{r}
# Function to process time data
time_sum <- function(df, prefix) {
  
  # Select specific columns
  selected_columns <- df %>%
    select(matches(paste0("^", prefix, " - Q[1-6] Time_Page Submit$")))
  
  # Converting character vectors to numeric
  data_numeric <- lapply(selected_columns, function(column) as.numeric(column))
  
  # Combine the lists into a data frame to facilitate row-wise operations
  data_numeric_df <- as.data.frame(data_numeric)
  
  # Filter out rows where all values are NA
  data_filtered <- data_numeric_df[rowSums(is.na(data_numeric_df)) != ncol(data_numeric_df), ]
  
  # List to store sums of each index across columns
  sums <- numeric(nrow(data_filtered))
  
  # Calculate and store sums of each index across columns
  for (i in seq_along(sums)) {
    sums[i] <- sum(data_filtered[i, ], na.rm = TRUE)
  }
  
  return(sums)
}
```

### Extra: Box Plots

Optional function to see data distribution for provided prefix, for visualization purposes only.

TODO: adjust y-scales for larger values. Plots are almost useless without that.

```{r}
box_plot <- function(bp_data){
  # Plot weighted accuracy
  ggboxplot(bp_data, x="metric", y="value",
            color = "metric", palette=c("#00AFBB","#E7B800"),
            ylab= "Value", xlab="Metric")
  
 #print(bp_data)
}
```

### Extra: Bar Graph

Optional function to see distribution of aggregated mean values for a language group.

```{r}
bar_plot <- function(data, title){
  ggplot(data, aes(x = orientation, y = metric, fill = orientation)) + 
    geom_bar(stat = "identity") + 
    labs(title = title, x = "Orientation", y = "Mean Value") +
    theme_minimal() + 
    scale_fill_brewer(palette="Accent")
}
```

***Q: What orientation does \<LANGUAGE\> do better with?***

# English (Primary Language)

Analyzing performance who chose English as their primary (/ native/ first) language. Calculations and statistical testing to *figure out what orientation (TB, LR, or RL) is best for the English language*.

```{r echo=FALSE}
participant_ID <- rep(1:eng_primary_size, times=2)

#TODO: shift to where global variables are defined above. 
```

### LEFT-RIGHT

Uses functions defined above to aggregate data - time and accuracy sums - for the English Left-Right orientation. Implements the **Shapiro Wilk test** to determine if data is normally distributed, assuming alpha = 0.05.

\*Uses columns **ELR3 and ELR4** in dataset for this purpose.

```{r}
#Calculating weighted accuracy
ELR34_acc <- acc_sum(pilotDF, "ELR[34]")
#print("LR Accuracy Normality Check")
shapiro.test(ELR34_acc)

#Summing times
ELR34_time <- time_sum(pilotDF, "ELR[34]")
shapiro.test(ELR34_time)

#creating df
ELR34_df <- data.frame(
  p_id = participant_ID,
  metric = rep(c("time", "accuracy"), each=eng_primary_size),
  value = c(ELR34_time,ELR34_acc)
)

# box blot distribution
#box_plot(ELR34_df)
```

### RIGHT - LEFT

Uses functions defined above to aggregate data - time and accuracy sums - for the English Right-Left orientation. Implements the **Shapiro Wilk test** to determine if data is normally distributed, assuming alpha = 0.05.

\*Uses columns **ERL3 and ERL4** in dataset for this purpose.

```{r}
#Calculating weighted accuracy
ERL34_acc <- acc_sum(pilotDF, "ERL[34]")
#print("RL Accuracy Normality Check")
shapiro.test(ERL34_acc)

#Summing times
ERL34_time <- time_sum(pilotDF, "ERL[34]")
#print("RL Time Normality Check")
shapiro.test(ERL34_time)

#creating df for plot
ERL34_df <- data.frame(
  p_id = participant_ID,
  metric = rep(c("time", "accuracy"), each=eng_primary_size),
  value = c(ERL34_time, ERL34_acc)
)

# box blot distribution
#box_plot(ERL34_df)
```

### TOP - BOTTOM

Uses functions defined above to aggregate data - time and accuracy sums - for the English Top-Bottom orientation. Implements the **Shapiro Wilk test** to determine if data is normally distributed, assuming alpha = 0.05.

\*Uses columns **ETB3 and ETB4** in dataset for this purpose.

```{r}
#Calculating weighted accuracy
ETB34_acc <- acc_sum(pilotDF, "ETB[34]")
#print("TB Accuracy Normality Check")
shapiro.test(ETB34_acc)

#Summing times
ETB34_time <- time_sum(pilotDF, "ETB[34]")
#print("TB Time Normality Check")
shapiro.test(ETB34_time)

#creating df for plot
ETB34_df <- data.frame(
  p_id = participant_ID,
  metric = rep(c("time", "accuracy"), each=eng_primary_size),
  value = c(ETB34_time, ETB34_acc)
)

# box blot distribution
#box_plot(ERL34_df)
```

#### Bar Plot(s) [extra]

```{r echo=FALSE}

mean_time_data <- data.frame(
  orientation=c("LR","TB","RL"),
  metric = c(mean(ELR34_time, na.rm = TRUE), mean(ETB34_time, na.rm = TRUE), mean(ERL34_time, na.rm = TRUE))
)

mean_acc_data <- data.frame(
  orientation=c("LR","TB","RL"),
  metric = c(mean(ELR34_acc, na.rm = TRUE), mean(ETB34_acc, na.rm = TRUE), mean(ERL34_acc, na.rm = TRUE))
)

bar_plot(mean_time_data,paste("Mean of Time Spent (in seconds) - English; participants:", eng_primary_size))
bar_plot(mean_acc_data, paste("Mean of Scored Accuracy - English; participants:", eng_primary_size))
```

### Merging Data (LR, RL, TB)

Merging data from all three orientations in to one data frame for statistical t-testing. A preview of how the frame looks like can be seen below.

```{r echo=FALSE}
# Merge the data frames
df_ENG <- ELR34_df %>%
  rename(value_LR = value) %>%
  full_join(ERL34_df %>% rename(value_RL = value), by = c("p_id", "metric")) %>%
  full_join(ETB34_df %>% rename(value_TB = value), by = c("p_id", "metric"))

# display merged data frame
head(df_ENG)

```

## Paired t-test (two-tailed) for ACCURACY

ASSUMING NORMALITY OF ALL DATA.

***TODO: CORRECTION FOR MULTIPLE COMPARISONS ?.***

Pairs:

-   ELR vs. ERL

-   ERL vs. ETB

-   ETB vs. ELR

**t-test: ELR vs. ERL accuracy**

**Null Hyp. :** There is no significant difference in the accuracy scores between a LR orientation and a RL orientation.

**Alternative Hyp. :** There is a significant difference in the accuracy scores between a LR orientation and a RL orientation.

*Assumed significance level/ alpha: 0.05*

```{r echo=FALSE}
#t-test: ELR vs. ERL accuracy

test_elr_erl_acc <- t.test(
  df_ENG %>% filter(metric=="accuracy") %>% pull(value_LR),
  df_ENG %>% filter(metric=="accuracy") %>% pull(value_RL),
  paired = TRUE
)

print(test_elr_erl_acc)
```

**t-test: ETB vs. ELR accuracy**

**Null Hyp. :** There is no significant difference in the accuracy scores between a LR orientation and a TB orientation.

**Alternative Hyp. :** There is a significant difference in the accuracy scores between a LR orientation and a TB orientation.

*Assumed significance level/ alpha: 0.05*

```{r echo=FALSE}
#t-test: ETB vs. ELR accuracy

test_etb_elr_acc <- t.test(
  df_ENG %>% filter(metric=="accuracy") %>% pull(value_LR),
  df_ENG %>% filter(metric=="accuracy") %>% pull(value_TB),
  paired = TRUE
)

print(test_etb_elr_acc)
```

**t-test: ERL vs. ETB accuracy**

**Null Hyp. :** There is no significant difference in the accuracy scores between a TB orientation and a RL orientation.

**Alternative Hyp. :** There is a significant difference in the accuracy scores between a TB orientation and a RL orientation.

*Assumed significance level/ alpha: 0.05*

```{r echo=FALSE}
#t-test: ERL vs. ETB accuracy

test_erl_etb_acc <- t.test(
  df_ENG %>% filter(metric=="accuracy") %>% pull(value_RL),
  df_ENG %>% filter(metric=="accuracy") %>% pull(value_TB),
  paired = TRUE
)

print(test_erl_etb_acc)
```

## Paired t-test for TIME

ASSUMING NORMALITY OF ALL DATA.

**t-test: ELR vs. ERL time**

**Null Hyp. :** There is no significant difference in the time taken to complete tasks between a LR orientation and a RL orientation.

**Alternative Hyp. :** There is a significant difference in the time taken to complete tasks between a LR orientation and a RL orientation.

*Assumed significance level/ alpha: 0.05*

```{r echo=FALSE}
#t-test: ELR vs. ERL time

test_elr_erl_time <- t.test(
  df_ENG %>% filter(metric=="time") %>% pull(value_LR),
  df_ENG %>% filter(metric=="time") %>% pull(value_RL),
  paired = TRUE
)

print(test_elr_erl_time)
```

```{r}
#means
paste("LR Time Mean:",mean(ELR34_time, na.rm = TRUE))
paste("RL Time Mean:",mean(ERL34_time, na.rm = TRUE))
```

**t-test: ETB vs. ELR time**

**Null Hyp. :** There is no significant difference in the time taken to complete tasks between a TB orientation and a LR orientation.

**Alternative Hyp. :** There is a significant difference in the time taken to complete tasks between a TB orientation and a LR orientation.

*Assumed significance level/ alpha: 0.05*

```{r echo=FALSE}
#t-test: ETB vs. ELR time

test_etb_elr_time <- t.test(
  df_ENG %>% filter(metric=="time") %>% pull(value_LR),
  df_ENG %>% filter(metric=="time") %>% pull(value_TB),
  paired = TRUE
)

print(test_etb_elr_time)
```

**t-test: ERL vs. ETB time**

**Null Hyp. :** There is no significant difference in the time taken to complete tasks between a TB orientation and a RL orientation.

**Alternative Hyp. :** There is a significant difference in the time taken to complete tasks between a TB orientation and a RL orientation.

*Assumed significance level/ alpha: 0.05*

```{r echo=FALSE}
#t-test: ERL vs. ETB time

test_erl_etb_time <- t.test(
  df_ENG %>% filter(metric=="time") %>% pull(value_RL),
  df_ENG %>% filter(metric=="time") %>% pull(value_TB),
  paired = TRUE
)

print(test_erl_etb_time)
```

# Urdu

Analyzing performance who chose Urdu as their primary (/ native/ first) language. Calculations and statistical testing to *figure out what orientation (TB, LR, or RL) is best for the Urdu language*.

```{r echo=FALSE}
participant_ID <- rep(1:urdu_primary_size, times=2)
```

### LEFT-RIGHT

Uses functions defined above to aggregate data - time and accuracy sums - for the Urdu Left-Right orientation. Implements the **Shapiro Wilk test** to determine if data is normally distributed, assuming alpha = 0.05.

\*Uses columns **ULR1 and ULR2** in dataset for this purpose.

```{r}
#Calculating weighted accuracy
ULR12_acc <- acc_sum(pilotDF, "ULR[12]")
#print("LR Accuracy Normality Check")
shapiro.test(ULR12_acc)

#Summing times
ULR12_time <- time_sum(pilotDF, "ULR[12]")
shapiro.test(ULR12_time)

#creating df
ULR12_df <- data.frame(
  p_id = participant_ID,
  metric = rep(c("time", "accuracy"), each=urdu_primary_size),
  value = c(ULR12_time,ULR12_acc)
)

# box blot distribution
#box_plot(ULR12_df)
```

### RIGHT - LEFT

Uses functions defined above to aggregate data - time and accuracy sums - for the Urdu Right-Left orientation. Implements the **Shapiro Wilk test** to determine if data is normally distributed, assuming alpha = 0.05.

\*Uses columns **URL1 and URL2** in dataset for this purpose.

```{r}
#Calculating weighted accuracy
URL12_acc <- acc_sum(pilotDF, "URL[12]")
#print("RL Accuracy Normality Check")
shapiro.test(URL12_acc)

#Summing times
URL12_time <- time_sum(pilotDF, "URL[12]")
#print("RL Time Normality Check")
shapiro.test(URL12_time)

#creating df for plot
URL12_df <- data.frame(
  p_id = participant_ID,
  metric = rep(c("time", "accuracy"), each=urdu_primary_size),
  value = c(URL12_time, URL12_acc)
)

# box blot distribution
#box_plot(URL12_df)
```

### TOP - BOTTOM

Uses functions defined above to aggregate data - time and accuracy sums - for the Urdu Top-Bottom orientation. Implements the **Shapiro Wilk test** to determine if data is normally distributed, assuming alpha = 0.05.

\*Uses columns **UTB1 and UTB2** in dataset for this purpose.

```{r}
#Calculating weighted accuracy
UTB12_acc <- acc_sum(pilotDF, "UTB[12]")
#print("TB Accuracy Normality Check")
shapiro.test(UTB12_acc)

#Summing times
UTB12_time <- time_sum(pilotDF, "UTB[12]")
#print("TB Time Normality Check")
shapiro.test(UTB12_time)

#creating df for plot
UTB12_df <- data.frame(
  p_id = participant_ID,
  metric = rep(c("time", "accuracy"), each=urdu_primary_size),
  value = c(UTB12_time, UTB12_acc)
)

# box blot distribution
#box_plot(URL12_df)
```

#### Bar Plot(s) [extra]

```{r echo=FALSE}

mean_time_data <- data.frame(
  orientation=c("LR","TB","RL"),
  metric = c(mean(ULR12_time, na.rm = TRUE), mean(UTB12_time, na.rm = TRUE), mean(URL12_time, na.rm = TRUE))
)

mean_acc_data <- data.frame(
  orientation=c("LR","TB","RL"),
  metric = c(mean(ULR12_acc, na.rm = TRUE), mean(UTB12_acc, na.rm = TRUE), mean(URL12_acc, na.rm = TRUE))
)

bar_plot(mean_time_data,paste("Mean of Time Spent (in seconds) - Urdu; participants:", urdu_primary_size))
bar_plot(mean_acc_data, paste("Mean of Scored Accuracy - Urdu; participants:", urdu_primary_size))
```

### Merging Data (LR, RL, TB)

Merging data from all three orientations in to one data frame for statistical t-testing. A preview of how the frame looks like can be seen below.

```{r echo=FALSE}
# Merge the data frames
df_URDU <- ULR12_df %>%
  rename(value_LR = value) %>%
  full_join(URL12_df %>% rename(value_RL = value), by = c("p_id", "metric")) %>%
  full_join(UTB12_df %>% rename(value_TB = value), by = c("p_id", "metric"))

# display merged data frame
head(df_URDU)

```

# Arabic

Analyzing performance who chose Arabic as their primary (/ native/ first) language. Calculations and statistical testing to *figure out what orientation (TB, LR, or RL) is best for the Arabic language*.

```{r echo=FALSE}
participant_ID <- rep(1:arb_primary_size, times=2)
```

### LEFT-RIGHT

Uses functions defined above to aggregate data - time and accuracy sums - for the Arabic Left-Right orientation. Implements the **Shapiro Wilk test** to determine if data is normally distributed, assuming alpha = 0.05.

\*Uses columns **ALR1 and ALR2** in dataset for this purpose.

```{r}
#Calculating weighted accuracy
ALR12_acc <- acc_sum(pilotDF, "ALR[12]")
#summary(ALR12_acc)
#print("LR Accuracy Normality Check")
shapiro.test(ALR12_acc)

#Summing times
ALR12_time <- time_sum(pilotDF, "ALR[12]")
shapiro.test(ALR12_time)

#creating df
ALR12_df <- data.frame(
  p_id = participant_ID,
  metric = rep(c("time", "accuracy"), each=arb_primary_size),
  value = c(ALR12_time,ALR12_acc)
)

# box blot distribution
#box_plot(ALR12_df)
```

### RIGHT - LEFT

Uses functions defined above to aggregate data - time and accuracy sums - for the Arabic Right-Left orientation. Implements the **Shapiro Wilk test** to determine if data is normally distributed, assuming alpha = 0.05.

\*Uses columns **ARL1 and ARL2** in dataset for this purpose.

```{r}
#Calculating weighted accuracy
ARL12_acc <- acc_sum(pilotDF, "ARL[12]")
#print("RL Accuracy Normality Check")
shapiro.test(ARL12_acc)

#Summing times
ARL12_time <- time_sum(pilotDF, "ARL[12]")
#print("RL Time Normality Check")
shapiro.test(ARL12_time)

#creating df for plot
ARL12_df <- data.frame(
  p_id = participant_ID,
  metric = rep(c("time", "accuracy"), each=arb_primary_size),
  value = c(ARL12_time, ARL12_acc)
)

# box blot distribution
#box_plot(ARL12_df)
```

### TOP - BOTTOM

Uses functions defined above to aggregate data - time and accuracy sums - for the Arabic Top-Bottom orientation. Implements the **Shapiro Wilk test** to determine if data is normally distributed, assuming alpha = 0.05.

\*Uses columns **ATB1 and ATB2** in dataset for this purpose.

```{r}
#Calculating weighted accuracy
ATB12_acc <- acc_sum(pilotDF, "ATB[12]")
#print("TB Accuracy Normality Check")
shapiro.test(ATB12_acc)

#Summing times
ATB12_time <- time_sum(pilotDF, "ATB[12]")
#print("TB Time Normality Check")
shapiro.test(ATB12_time)

#creating df for plot
ATB12_df <- data.frame(
  p_id = participant_ID,
  metric = rep(c("time", "accuracy"), each=arb_primary_size),
  value = c(ATB12_time, ATB12_acc)
)

# box blot distribution
#box_plot(ARL12_df)
```

#### Bar Plot(s) [extra]

```{r echo=FALSE}

mean_time_data <- data.frame(
  orientation=c("LR","TB","RL"),
  metric = c(mean(ALR12_time, na.rm = TRUE), mean(ATB12_time, na.rm = TRUE), mean(ARL12_time, na.rm = TRUE))
)

mean_acc_data <- data.frame(
  orientation=c("LR","TB","RL"),
  metric = c(mean(ALR12_acc, na.rm = TRUE), mean(ATB12_acc, na.rm = TRUE), mean(ARL12_acc, na.rm = TRUE))
)

bar_plot(mean_time_data,paste("Mean of Time Spent (in seconds) - Arabic; participants:", arb_primary_size))
bar_plot(mean_acc_data, paste("Mean of Scored Accuracy - Arabic; participants:", arb_primary_size))
```

### Merging Data (LR, RL, TB)

Merging data from all three orientations in to one data frame for statistical t-testing. A preview of how the frame looks like can be seen below.

```{r echo=FALSE}
# Merge the data frames
df_ARABIC <- ALR12_df %>%
  rename(value_LR = value) %>%
  full_join(ARL12_df %>% rename(value_RL = value), by = c("p_id", "metric")) %>%
  full_join(ATB12_df %>% rename(value_TB = value), by = c("p_id", "metric"))

# display merged data frame
head(df_ARABIC)
```

# Unpaired t-tests - TIME

ASSUMING NORMALITY OF ALL DATA.

**ASSUMES EQUAL VARIANCE - FTEST NEEDED.**

F-TEST also assumes normality.

***What \<LANG\> is best for \<ORIENTATION\> (LR, RL, TB)?***

Pairs:

-   For all 3 orientations: (9 tests)

    -   Urdu vs Eng

    -   Eng vs Arb

    -   Arb vs. Urdu
